Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-07-03 WRITEUP/ms.tex
added a not quite gratuitous reference to Garland et al 2015

% --------------------------------------------

% AP: I have some compatibility issues with the new style (i.e. \section does not work)
\IfFileExists{emulateapjlegacy.cls}{\documentclass[iop]{emulateapjlegacy}}{\documentclass[iop]{emulateapj}}

@@

\section{Introduction}
The growth of galaxies and their subsequent evolution are governed by the baryon cycle---galaxies accrete gas from the intergalactic medium (IGM) either directly from the cosmic web, or through mergers with other galaxies. This gas fuels \SF and feeds central
supermassive black holes. Subsequent feedback replenishes and enriches the circumgalactic medium by expelling some
part of this material.
Existing studies indicated that early galaxies are more gas-rich with molecular fractions higher than
those of present-day galaxies \citep[e.g.,][]{vandevoort11b, Decarli16a, Decarli17a}. 
Massive gas inflows from the IGM trigger gravitational instabilities that lead to the formation of molecular cloud complexes (MCCs)
that are typically more massive ($M_{\rm gas}\simeq 10^9$\,\Msun) and extended ($\simeq$ sub-kpc) than those observed in nearby galaxies (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
Some theoretical works argue that the migration of such giant massive clumps are largely responsible for the buildup of the bulges of massive galaxies at redshift \z$\sim$\,0 \citep[e.g.,][]{Ceverino10a}.

@@

FIR fine-structure lines (e.g., \cii, \nii, and \oiii), and CO and [\ci]~lines are key diagnostics for constraining the ISM conditions of galaxies. They also provide highly complementary information on different ISM phases (ionized, atomic, molecular; e.g., \citealt{Scoville74a, Rubin85a, Malhotra01a}).
%
Global measurements of these diagnostics in \highz galaxies have provided preliminary information on their global properties (e.g., gas masses, gas temperature, and radiation field intensity). However, spatially resolving their ISM is necessary to fully understand many aspects of galaxy evolution and the physics behind their intense \SF (SFR\ssim100$-$3000\,\Msun\,yr\pmOne; 
see e.g., the review by \citealt{CW13}).
%
To date, spatially resolved ISM properties of \highz galaxies have only been mapped in a handful of 
galaxies at high redshift using tracers such as dust continuum, CO, and \cii lines (e.g., \citealt{Swinbank11a, Hodge15a, Ferkinhoff15a, 
Hodge16a, Leung19a}). These studies find that galaxies close to the peak of cosmic \SF ($z$\ssim2) are more molecular gas-rich, turbulent, and clumpy than nearby galaxies.

>>>>

% --------------------------------------------
%mm2 edits of 3 Jul 19 marked like this M-MML
% AP: I have some compatibility issues with the new style (i.e. \section does not work)
\IfFileExists{emulateapjlegacy.cls}{\documentclass[iop]{emulateapjlegacy}}{\documentclass[iop]{emulateapj}}

@@

\section{Introduction}
The growth of galaxies and their subsequent evolution are governed by the baryon cycle---galaxies accrete gas from the intergalactic medium (IGM) either directly from the cosmic web, or through mergers with other galaxies. This gas fuels \SF and feeds central
supermassive black holes. Subsequent feedback replenishes and enriches the circumgalactic medium by expelling some
part of this material.
Existing studies indicate that early galaxies are more gas-rich with molecular fractions higher than
those of present-day galaxies \citep[e.g.,][]{vandevoort11b, Decarli16a, Decarli17a}. 
Massive gas inflows from the IGM trigger gravitational instabilities that lead to the formation of molecular cloud complexes (MCCs)
that are typically more massive ($M_{\rm gas}\simeq 10^9$\,\Msun) and extended ($\simeq$ sub-kpc) than those observed in nearby galaxies (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
Some theoretical works argue that the migration of such giant massive clumps are largely responsible for the buildup of the bulges of massive galaxies at redshift \z$\sim$\,0 \citep[e.g.,][]{Ceverino10a}.

@@

FIR fine-structure lines (e.g., \cii, \nii, and \oiii), and CO and [\ci]~lines are key diagnostics for constraining the ISM conditions of galaxies. They also provide highly complementary information on different ISM phases (ionized, atomic, molecular; e.g., \citealt{Scoville74a, Rubin85a, Malhotra01a}).
%
Global measurements of these diagnostics in \highz galaxies have provided preliminary information on their global properties (e.g., gas masses, gas temperature, and radiation field intensity). However, spatially resolving their ISM is necessary to fully understand many aspects of galaxy evolution and the physics behind their intense \SF (SFR\ssim100$-$3000\,\Msun\,yr\pmOne; 
see e.g., the review by \citealt{CW13}).
%
To date, spatially resolved ISM properties of \highz galaxies have only been mapped in a handful of 
galaxies at high redshift using tracers such as dust continuum, CO, and \cii lines (e.g., \citealt{Swinbank11a, Hodge15a, Ferkinhoff15a, 
Hodge16a, Leung19a}). These studies find that galaxies close to the
peak of cosmic \SF ($z$\ssim2) are more molecular gas-rich, turbulent,
and clumpy than nearby galaxies,
% mm2
    although luminous compact blue galaxies may represent local
    analogs of these gas-rich, clumpy systems \citep{Garland15}.
